---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MSCCT

<!-- badges: start -->
<!-- badges: end -->

Multiple Survival Crossing Curves Tests

This package contains tests for comparison or two or more survival curves when the
proportional hazards hypothesis is not verified, in particular when the survival
curves cross each other.

## Installation

You can install the development version of MSCCT from [GitHub](https://github.com/) with:

``` {r eval=FALSE}
devtools::install_github("https://github.com/HMinP/MSCCT")
```

## Example

```{r}
library(MSCCT)
```


This package contains:

- The weighted log-rank test

The log-rank test compares for each group and for each time of event the expected and the observed number
of events. The weighted log-rank adds weights to each time of event. Some (implemented)
exemples are the Flemming-Harrington test and the Gehan-Wilcoxon test.  It is also possible to chose
the weights you want.

```{r}
multiLR(data_under_PH)
```

```{r}
multiLR(data_under_PH, weights=numeric(), test="fh", rho=1, gamma=0)
```

- The Restricted Mean Survival Test

The Restricted Mean Survival Time at time $\tau$ is the area under a survival curve
up to time $\tau$. The RMST test compares the areas under the survival curves and
tests the equality to zero of the difference of RMST.

```{r}
multirmst(data_under_PH, tau=12)
```



















