---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MSCCT

<!-- badges: start -->
<!-- badges: end -->

This package contains tests for comparison or two or more survival curves when the
proportional hazards hypothesis is not verified, in particular when the survival
curves cross each other.

## Installation

You can install the development version of MSCCT from [GitHub](https://github.com/) with:

``` {r eval=FALSE}
devtools::install_github("https://github.com/HMinP/MSCCT")
```

## Example

```{r}
library(MSCCT)
```


This package contains:

- The weighted log-rank test

Compares for each group and for each time of event the expected and the observed number
of events. The weighted log-rank adds weights to each time of event. Some (implemented)
exemples are the Flemming-Harrington test and the Gehan-Wilcoxon test.  It is also possible to chose
the weights you want.

```{r}
multiLR(data_under_PH)
```

```{r}
multiLR(data_under_PH, weights=numeric(), test="fh", rho=1, gamma=0)
```




















